---
title: "Final Project"
author: "Lihao Liu, Zikang Chen, Hinn Zhang"
output: 
  html_document:
    toc: true
    toc_float: true
---

## R Markdown

Here we will load all the packages we need for this project.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(skimr)
```

## Introduction



## Questions

1. Does a movie released during a holiday season tend to receive a lower rating?

## Data

The data set we are going to explore is about Netflix Movies and TV Shows. 

### Data Import

Here we will import the csv file into the studio and take a look at the data set:

```{r}
data <- read_csv("netflix_titles.csv")
movies <- read_csv("n_movies.csv")
glimpse(data)
glimpse(movies)
```

### Data Wrangling

First, we will merge the two data sets so as to get each movie's rating and votes and also leave only movies with us, since we are not considering TV shows.

```{r}
#filter out only movies
data <- data |> filter(type == "Movie")

#get only the rating and voting columns
movies <- movies[, c("title", "rating", "votes")]

#merge the two data sets
merged <- merge(data, movies, by = "title")
glimpse(merged)
```

```{r}
# rename columns
merged <- merged |>
  rename("certificate" = "rating.x",
         "rating" = "rating.y")

# convert dates from character to date type
merged$date_added <- mdy(merged$date_added)

# create a month column
merged$month <- month(merged$date_added)
```

```{r}

```


## Analysis

### Exploratory Data Analysis

```{r}
merged |>
  ggplot(aes(x = release_year)) +
  geom_bar() +
  labs(x = "Year released",
       y = "Number of movies",
       title = "Most movies released after 2010s") +
  theme(text = element_text(size = 15),
        plot.title.position = "plot")
```

```{r}
merged |>
  ggplot(aes(x = rating)) +
  geom_bar() +
  labs(x = "Audience rating",
       y = "Number of movies",
       title = "Most movies receive rating of 5 - 7") +
  theme(text = element_text(size = 15),
        plot.title.position = "plot")
```

```{r}
merged |>
  ggplot(aes(x = month)) +
  geom_bar() +
  labs(x = "Month added",
       y = "Number of movies",
       title = "Movies are added all year round to Netflix") +
  scale_x_continuous(breaks = seq(1, 12)) +
  theme(text = element_text(size = 15),
        plot.title.position = "plot")
```

### Data Analysis



### Results


## Conclusion



